A non-contextual hidden variable model for QM

### 2016-07-06 finalPaper.tex
Made minor updates after a small discussion with Prof Arvind

\begin{notn} (a) $\psi\in\mathcal{H}$ would typically represent the quantum mechanical state of the system (assumed pure), residing in the Hilbert space $\mathcal{H}$, (b) $\hat{\mathcal{H}}$ is defined to mean $\mathcal{H}\otimes\mathcal{H}^{\dagger}$ (i.e. the set of Hermitian operators, observables, on the space $\mathcal{H}$), (c) $[\mathcal{H}]$ is defined to mean $(\mathcal{H},\,\mathbb{R}^{\otimes})$, which represents the state of the system including hidden variables, (d) $[\psi]\in[\mathcal{H}]$ will represent the state of the system, including hidden variables, (e) a prediction map is $m:\hat{\mathcal{H}},[\mathcal{H}]\to\mathbb{R}$, (f) a sequence map is $s:\hat{\mathcal{H}},[\mathcal{H}],\mathbb{R}\to[\mathcal{H}]$, (g) the set of all experimental setups is denoted by $\mathcal{E}$, (h) a setup map is $e:\hat{\mathcal{H}}\to\mathcal{E}$, (i) number of observables is represented by $N \in \mathbb{Z}^+$, (j) $f$ is an arbitrary map from $\hat{\mathcal{H}}^{\otimes N}\to \hat{\mathcal{H}}$ constructed using multiplication and addition of the observables, and multiplication with complex numbers\footnote{Strictly, the map $f$ would depend on the operators to ensure preservation of Hermiticity; thus a given $f$ will be defined only for a subset of $\hat {\mathcal H}^{\otimes N}$.}, (k) $\tilde{f}$ is a map from $\mathbb{R}^{\otimes N} \to \mathbb{R}$ constructed by replacing observables in $f$ with real numbers\footnote{$\tilde f$ constructed this way should strictly be written as $\tilde f:\mathbb{R}^{\otimes N} \to \mathbb{C}$.}.
\end{notn}

@@

In the literature broader definitions have been suggested which declare a larger set of theories as non-contextual. For our purposes however, this restricted definition will suffice. The term contextual is used to suggest that the value an operator takes might depend on which other compatible observable it is measured with. Since quantum mechanics (QM) yields deterministic results only in specific situations, it is imperative to analyse the meaning of contextuality by `completing' QM. Hidden variable theories do precisely this and we have at our disposal the heretic theory of Bohm. Circumventing the details of the theory, we note its salient feature; with each particle, one associates precisely defined $(q,p)$ and a wavefunction $\psi$. Consequently, the outcomes of all experiment are predictable, granted the initial conditions of the system and the apparatus are known (the `hidden variables'). The essence of Bohmian Mechanics relevant here can be captured by the following theorem.

@@

\begin{align*}
& m(f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{N}),[\psi]) = \\
& \tilde f(m(\hat{B}_{1},[\psi]),m(\hat{B}_{2},[\psi]),\dots m(\hat{B}_{N},[\psi])),
\end{align*}
where $\hat{B}_{i}\in\hat{\mathcal{H}}$ are arbitrary mutually commuting observables and $[\psi]\in[\mathcal{H}]$. A non-\emph{multiplicative} map is one that is not multiplicative.
\end{defn}
Note that if $m$ is taken to represent the measurement outcome (in
QM), then for states of the system which are simultaneous eigenkets
of $\hat{B}_{i}$s, $m$ must clearly be multiplicative. It is, however,
not obvious that this property must always hold. To motivate this,
consider the state of two spin half particles, $\left|11\right\rangle :=\left|1\right\rangle \otimes\left|1\right\rangle $
written in the computational basis, $\hat{B}_{1}=\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}$,
$\hat{B}_{2}=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}$ and $\hat{C}=\hat{B}_{1}\hat{B}_{2}=-\hat{\sigma}_{z}\otimes\hat{\sigma}_{z}$,
we have $m(\hat{C})=-1$ while $m(\hat{B}_{1})=\pm1$ and $m(\hat{B}_{2})=\pm1$,
independently, according to QM, with probability half. Antithetically it is clear that if one first measures
$\hat{B}_{1}$ and subsequently measures $\hat{B}_{2}$, then the
product of the results must be $-1$. This is consistent with measuring
$\hat{C}$. To capture this property we define \emph{sequential multiplicativity}
as follows.
\begin{defn}
A prediction map $m$ is \emph{sequentially multiplicative} for a
given sequence map $s$, iff 
\begin{align*}
&m(f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{N}),[\psi_{1}])=\\
&\tilde f(m(\hat{B}_{1},[\psi_{k_{1}}]),m(\hat{B}_{2},[\psi_{k_{2}}]),\dots,m(\hat{B}_{N},[\psi_{k_{N}}])),
\end{align*}
where $\mathbf{k}=(k_{1},k_{2},\dots,k_{N})\in\{(1,2,3\dots N),(2,1,3\dots N)$ + permutations, making $N!$ terms$\}$,
$\hat{B}_{i}\in\hat{\mathcal{H}}$ are arbitrary mutually commuting
observables, $[\psi_{i}]\in[\mathcal{H}]$ and $[\psi_{k+1}]\equiv s(\hat{B}_{k},[\psi_{k}],m(\hat{B}_{k},[\psi_{k}]))$,
$\forall\,[\psi_{i}]$.
\end{defn}
We now discuss the `proofs of contextuality' in the purview of the
aforesaid.
\begin{thm}
Let a map $m:\hat{\mathcal{H}}\to\mathbb{R}$, be s.t. (a) $m(\hat{\mathbb{I}})=1$,
(b) $m(f(\hat{A}_{1},\hat{A}_{2},\dots))=\tilde f(m(\hat{A}_{1}),m(\hat{A}_{2}),\dots)$,
where $\hat{A}_{i}$ are arbitrary Hermitian operators. If $m$ is assumed to describe the outcomes of measurements, then no $m$ exists which is consistent with all predictions of Quantum Mechanics.\label{thm:det} \end{thm}
Here $m$ maybe viewed as a specific class of prediction maps, that
implicitly depends on the state $[\psi]$. It follows then that the
maps ruled out by the theorem are non-contextual. The set of maps
ruled out, however, can be enlarged by imposing fewer restrictions
on it. This is achieved by the following theorem.

@@

Before proceeding we note, however, that QM enforces \emph{sequential
multiplicativity} at least in certain cases. This result will be used
to assess accuracy of any hidden variable model we might propose.
\begin{prop*}
Let the system be in a state, s.t. measurement of $\hat{C}$ yields
repeatable results (same result each time). Then according to QM,
\emph{sequential multiplicativity} holds, where $\hat{C}\equiv f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n})$,
and $\hat{B}_{i}$ are as defined. \end{prop*}
\begin{proof}
Assume without loss of generality that $\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n}$
are mutually compatible (commuting) and complete set of operators.
If say for instance the set is not complete, then one can add the
missing operators and label them as aforesaid. It follows that $\exists$
$\left|\mathbf{b}=\left(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})}\right)\right\rangle $
s.t. $\hat{B}_{i}\left|\mathbf{b}\right\rangle =b_{i}^{(l_{i})}\left|\mathbf{b}\right\rangle $,
where $l_{i}$ indexes the eigenvalues corresponding to $\hat{B}_{i}$
and that $\sum_{\mathbf{b}}\left|\mathbf{b}\right\rangle \left\langle \mathbf{b}\right|=\hat{\mathbb{I}}$.
Let the state of the system be given by $\left|\psi\right\rangle $
and it must be s.t. $\hat{C}\left|\psi\right\rangle =c\left|\psi\right\rangle $,
by assumption. For the statement to follow, one need only show that
$\left|\psi\right\rangle $ must be made of only those $\left|\mathbf{b}\right\rangle $s,
which satisfy $c=\tilde f(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})})$.
This is the crucial step. Proving this is so is trivial. We start
with $\hat{C}\left|\psi\right\rangle =c\left|\psi\right\rangle $
and take its inner product with $\left\langle \mathbf{b}\right|$
to get 
\begin{eqnarray*}
\left\langle \mathbf{b}\right|\hat{C}\left|\psi\right\rangle  & = & c\left\langle \mathbf{b}|\psi\right\rangle ,\\
\left\langle \mathbf{b}\right|f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n})\left|\psi\right\rangle  & = & c\left\langle \mathbf{b}|\psi\right\rangle ,\\
\tilde f(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})})\left\langle \mathbf{b}|\psi\right\rangle  & = & c\left\langle \mathbf{b}|\psi\right\rangle .
\end{eqnarray*}
Also, we have $\left|\psi\right\rangle =\sum_{\mathbf{b}}\left\langle \mathbf{b}|\psi\right\rangle \left|\mathbf{b}\right\rangle $,
from completeness. If we consider $\left|\mathbf{b}\right\rangle $s
for which $\left\langle \mathbf{b}|\psi\right\rangle \neq0$, then we can conclude that indeed $c=\tilde f(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})})$.
However, when $\left\langle \mathbf{b}|\psi\right\rangle =0$, viz.
$\left|\mathbf{b}\right\rangle $s that are orthogonal to $\left|\psi\right\rangle $,
then nothing can be said. We can thus conclude that $\left|\psi\right\rangle $
is made only of those $\left|\mathbf{b}\right\rangle $s that satisfy
the required relation. That completes the proof.
\end{proof}
It is worth noting that in the PM case, where $\hat{R}_{i}$ and $\hat{C}_{j}$
are just $\pm\hat{\mathbb{I}}$, it follows that all states are their
eigenstates. Consequently, for these operators \emph{sequential multiplicativity}
must always hold.

@@

\begin{proof}
GHZ construction ($\left|\mathcal{H}\right|\ge6$): Consider three
observers with one particle each. Each observer can measure two properties,
call them X and Y, with outcomes $\pm1$. The associated operators
are $\hat{\sigma}_{x}$ and $\hat{\sigma}_{y}$. The state of the
system is $\sqrt{2}\left|\chi_{G}\right\rangle =\left|000\right\rangle -\left|111\right\rangle $
and we also define $\hat{A}:=\hat{\sigma}_{x}\otimes\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}$,
$\hat{A}\left|\chi_{G}\right\rangle =\left|\chi_{G}\right\rangle $,
$\hat{B}:=\hat{\sigma}_{y}\otimes\hat{\sigma}_{x}\otimes\hat{\sigma}_{y}$
and $\hat{C}:=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}\otimes\hat{\sigma}_{z}$.
A measurement of $\hat{A}$ would correspond to measurement of property
$X,\,Y$ and $Y$ by the three observers respectively. For a map $m$
consistent with measurement outcomes of QM, we must have $m(\hat{A})=m(\hat{B})=m(\hat{C})=+1$.
Property (b) of the map $\implies1=m(\hat{A}\hat{B}\hat{C})=m(\hat{\sigma}_{x}\otimes\hat{\sigma}_{y}\hat{\sigma}_{x}\hat{\sigma}_{y}\otimes\hat{\sigma}_{x})=m(\hat{\sigma}_{x}^{(1)})m(\hat{\sigma}_{y}^{(2)}\hat{\sigma}_{x}^{(2)}\hat{\sigma}_{y}^{(2)})m(\hat{\sigma}_{x}^{(3)})=m(\hat{\sigma}_{x}^{(1)})m(\hat{\sigma}_{x}^{(2)})m(\hat{\sigma}_{x}^{(3)})=m(\hat{D}\equiv\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}),$
where $\hat{\sigma}_{x}^{(1)}\equiv\hat{\sigma}_{x}\otimes\hat{\mathbb{I}}\otimes\hat{\mathbb{I}}$
and so on. It must be stressed that although $\hat{A}$, $\hat{B}$
and $\hat{C}$ mutually commute, $\hat{\sigma}_{2}^{(2)},\hat{\sigma}_{y}^{(2)}$
do not. We used property (b) over both these sets of operators in
the previous step. Returning to the argument, note that $\hat{D}\left|\chi_{G}\right\rangle =-\left|\chi_{G}\right\rangle $,
$\implies m(\hat{D})=-1$ which yields a contradiction. We therefore
conclude that no $m$ with the said properties exists which is consistent
with all predictions of QM.
\end{proof}

>>>>

\begin{notn} (a) $\psi\in\mathcal{H}$ would typically represent the quantum mechanical state of the system (assumed pure), residing in the Hilbert space $\mathcal{H}$, (b) $\hat{\mathcal{H}}$ is defined to mean $\mathcal{H}\otimes\mathcal{H}^{\dagger}$ (i.e. the set of Hermitian operators, observables, on the space $\mathcal{H}$), (c) $[\mathcal{H}]$ is defined to mean $(\mathcal{H},\,\mathbb{R}^{\otimes})$, which represents the state of the system including hidden variables, (d) $[\psi]\in[\mathcal{H}]$ will represent the state of the system, including hidden variables, (e) a prediction map is $m:\hat{\mathcal{H}},[\mathcal{H}]\to\mathbb{R}$, (f) a sequence map is $s:\hat{\mathcal{H}},[\mathcal{H}],\mathbb{R}\to[\mathcal{H}]$, (g) the set of all experimental setups is denoted by $\mathcal{E}$, (h) a setup map is $e:\hat{\mathcal{H}}\to\mathcal{E}$, (i) number of observables is represented by $N \in \mathbb{Z}^+$, (j) $f$ is an arbitrary map from $\hat{\mathcal{H}}^{\otimes N}\to \hat{\mathcal{H}}$ constructed using multiplication and addition of the observables, and multiplication with complex numbers\footnote{Strictly, the map $f$ would depend on the operators to ensure preservation of Hermiticity; thus a given $f$ will be defined only for a subset of $\hat {\mathcal H}^{\otimes N}$.}, (k) $\tilde{f}$ is a map from $\mathbb{R}^{\otimes N} \to \mathbb{R}$ constructed by replacing observables in $f$ with real numbers\footnote{$\tilde f$ constructed this way should be written as $\tilde f:\mathbb{R}^{\otimes N} \to \mathbb{C}$. In fact the values should be restricted to the spectrum of the associated observables.}.
\end{notn}

@@

In the literature broader definitions have been suggested which declare a larger set of theories as non-contextual. For our purposes however, this restricted definition will suffice. The term contextual is used to suggest that the value an operator takes might depend on which other compatible observable it is measured with. Since quantum mechanics (QM) yields deterministic results only in specific situations, it is imperative to analyse the meaning of contextuality by `completing' QM. Hidden variable theories do precisely this and we have at our disposal the heretic theory of Bohm. Circumventing the details of the theory, we note its salient feature; with each particle, one associates precisely defined $(q,p)$ and a wavefunction $\psi$. The construction is such that the particles are guided by the wavefunction. Consequently, the outcomes of all experiment are predictable, granted the initial conditions of the system and the apparatus are known (the `hidden variables'). The essence of Bohmian Mechanics relevant here can be captured by the following theorem.

@@

\begin{align*}
& m(f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{N}),[\psi]) = \\
& \tilde f(m(\hat{B}_{1},[\psi]),m(\hat{B}_{2},[\psi]),\dots m(\hat{B}_{N},[\psi])),
\end{align*}
where $\hat{B}_{i}\in\hat{\mathcal{H}}$ are arbitrary mutually commuting observables and $[\psi]\in[\mathcal{H}]$. A non-\emph{multiplicative} map is one that is not multiplicative.
\end{defn}
Note that if $m$ is taken to represent the measurement outcome (in
QM), then for states of the system which are simultaneous eigenkets
of $\hat{B}_{i}$s, $m$ must clearly be multiplicative. It is, however,
not obvious that this property must always hold. To motivate this,
consider the state of two spin half particles, $\left|11\right\rangle :=\left|1\right\rangle \otimes\left|1\right\rangle $
written in the computational basis, $\hat{B}_{1}=\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}$,
$\hat{B}_{2}=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}$ and $\hat{C}=\hat{B}_{1}\hat{B}_{2}=-\hat{\sigma}_{z}\otimes\hat{\sigma}_{z}$,
we have $m(\hat{C})=-1$ while $m(\hat{B}_{1})=\pm1$ and $m(\hat{B}_{2})=\pm1$,
independently, according to QM, with probability half. Here multiplicativity doesn't seem to hold. Antithetically it is clear that if one first measures
$\hat{B}_{1}$ and subsequently measures $\hat{B}_{2}$, then the
product of the results must be $-1$. This is consistent with measuring
$\hat{C}$. To capture this property we define \emph{sequential multiplicativity}
as follows.
\begin{defn}
A prediction map $m$ is \emph{sequentially multiplicative} for a
given sequence map $s$, iff 
\begin{align*}
&m(f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{N}),[\psi_{1}])=\\
&\tilde f(m(\hat{B}_{1},[\psi_{k_{1}}]),m(\hat{B}_{2},[\psi_{k_{2}}]),\dots,m(\hat{B}_{N},[\psi_{k_{N}}])),
\end{align*}
where $\mathbf{k}=(k_{1},k_{2},\dots,k_{N})\in\{(1,2,3\dots N),(2,1,3\dots N)$ + permutations, making $N!$ terms$\}$,
$\hat{B}_{i}\in\hat{\mathcal{H}}$ are arbitrary mutually commuting
observables, $[\psi_{i}]\in[\mathcal{H}]$ and $[\psi_{k+1}]\equiv s(\hat{B}_{k},[\psi_{k}],m(\hat{B}_{k},[\psi_{k}]))$,
$\forall\,[\psi_{i}]$.
\end{defn}
We now discuss the `proofs of contextuality' in the purview of the
aforesaid.
\begin{thm}
Let a map $m:\hat{\mathcal{H}}\to\mathbb{R}$, be s.t. (a) $m(\hat{\mathbb{I}})=1$,
(b) $m(f(\hat{A}_{1},\hat{A}_{2},\dots))=\tilde f(m(\hat{A}_{1}),m(\hat{A}_{2}),\dots)$,
where $\hat{A}_{i}$ are arbitrary Hermitian operators. If $m$ is assumed to describe the outcomes of measurements, then no $m$ exists which is consistent with all predictions of Quantum Mechanics.\label{thm:det} \end{thm}
Here $m$ maybe viewed as a specific class of prediction maps, that
implicitly depends on the state $[\psi]$. It follows then that the
maps ruled out by the theorem are non-contextual. The set of maps
ruled out, however, can be enlarged by imposing fewer restrictions
on it. This is achieved by the following theorem.

@@

Before proceeding we note, however, that QM can enforce \emph{sequential multiplicativity}. This result will be used to assess accuracy of any hidden variable model we might propose.
\begin{prop*}
Let the system be in a state, s.t. measurement of $\hat{C}$ yields
repeatable results (same result each time). Then according to QM,
\emph{sequential multiplicativity} holds, where $\hat{C}\equiv f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n})$,
and $\hat{B}_{i}$ are as defined. \end{prop*}
\begin{proof}
Assume without loss of generality that $\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n}$
are mutually compatible (commuting) and complete set of operators.
If say for instance the set is not complete, then one can add the
missing operators and label them as aforesaid. It follows that $\exists$
$\left|\mathbf{b}=\left(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})}\right)\right\rangle $
s.t. $\hat{B}_{i}\left|\mathbf{b}\right\rangle =b_{i}^{(l_{i})}\left|\mathbf{b}\right\rangle $,
where $l_{i}$ indexes the eigenvalues corresponding to $\hat{B}_{i}$
and that $\sum_{\mathbf{b}}\left|\mathbf{b}\right\rangle \left\langle \mathbf{b}\right|=\hat{\mathbb{I}}$.
Let the state of the system be given by $\left|\psi\right\rangle $
and it must be s.t. $\hat{C}\left|\psi\right\rangle =c\left|\psi\right\rangle $,
by assumption. For the statement to follow, one need only show that
$\left|\psi\right\rangle $ must be made of only those $\left|\mathbf{b}\right\rangle $s,
which satisfy $c=\tilde f(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})})$.
This is the crucial step. Proving this is so is trivial. We start
with $\hat{C}\left|\psi\right\rangle =c\left|\psi\right\rangle $
and take its inner product with $\left\langle \mathbf{b}\right|$
to get 
\begin{eqnarray*}
\left\langle \mathbf{b}\right|\hat{C}\left|\psi\right\rangle  & = & c\left\langle \mathbf{b}|\psi\right\rangle ,\\
\left\langle \mathbf{b}\right|f(\hat{B}_{1},\hat{B}_{2},\dots\hat{B}_{n})\left|\psi\right\rangle  & = & c\left\langle \mathbf{b}|\psi\right\rangle ,\\
\tilde f(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})})\left\langle \mathbf{b}|\psi\right\rangle  & = & c\left\langle \mathbf{b}|\psi\right\rangle .
\end{eqnarray*}
Also, we have $\left|\psi\right\rangle =\sum_{\mathbf{b}}\left\langle \mathbf{b}|\psi\right\rangle \left|\mathbf{b}\right\rangle $,
from completeness. If we consider $\left|\mathbf{b}\right\rangle $s
for which $\left\langle \mathbf{b}|\psi\right\rangle \neq0$, then we can conclude that indeed $c=\tilde f(b_{1}^{(l_{1})},b_{2}^{(l_{2})},\dots b_{n}^{(l_{n})})$.
However, when $\left\langle \mathbf{b}|\psi\right\rangle =0$, viz.
$\left|\mathbf{b}\right\rangle $s that are orthogonal to $\left|\psi\right\rangle $,
then nothing can be said. We can thus conclude that $\left|\psi\right\rangle $
is made only of those $\left|\mathbf{b}\right\rangle $s that satisfy
the required relation. That completes the proof.
\end{proof}
It is worth noting that in the PM case, where $\hat{R}_{i}$ and $\hat{C}_{j}$
are just $\pm\hat{\mathbb{I}}$, it follows that all states are their
eigenstates. Consequently, for these operators \emph{sequential multiplicativity}
must always hold.

@@

\begin{proof}
GHZ construction ($\left|\mathcal{H}\right|\ge6$): Consider three
observers with one spin half particle each. Each observer can measure two properties,
call them X and Y, with outcomes $\pm1$. The associated operators
are $\hat{\sigma}_{x}$ and $\hat{\sigma}_{y}$. The state of the
system is $\sqrt{2}\left|\chi_{G}\right\rangle =\left|000\right\rangle -\left|111\right\rangle $
and we also define $\hat{A}:=\hat{\sigma}_{x}\otimes\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}$,
$\hat{A}\left|\chi_{G}\right\rangle =\left|\chi_{G}\right\rangle $,
$\hat{B}:=\hat{\sigma}_{y}\otimes\hat{\sigma}_{x}\otimes\hat{\sigma}_{y}$
and $\hat{C}:=\hat{\sigma}_{y}\otimes\hat{\sigma}_{y}\otimes\hat{\sigma}_{z}$.
A measurement of $\hat{A}$ would correspond to measurement of property
$X,\,Y$ and $Y$ by the three observers respectively. For a map $m$
consistent with measurement outcomes of QM, we must have $m(\hat{A})=m(\hat{B})=m(\hat{C})=+1$.
Property (b) of the map $\implies1=m(\hat{A}\hat{B}\hat{C})=m(\hat{\sigma}_{x}\otimes\hat{\sigma}_{y}\hat{\sigma}_{x}\hat{\sigma}_{y}\otimes\hat{\sigma}_{x})=m(\hat{\sigma}_{x}^{(1)})m(\hat{\sigma}_{y}^{(2)}\hat{\sigma}_{x}^{(2)}\hat{\sigma}_{y}^{(2)})m(\hat{\sigma}_{x}^{(3)})=m(\hat{\sigma}_{x}^{(1)})m(\hat{\sigma}_{x}^{(2)})m(\hat{\sigma}_{x}^{(3)})=m(\hat{D}\equiv\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}\otimes\hat{\sigma}_{x}),$
where $\hat{\sigma}_{x}^{(1)}\equiv\hat{\sigma}_{x}\otimes\hat{\mathbb{I}}\otimes\hat{\mathbb{I}}$
and so on. It must be stressed that although $\hat{A}$, $\hat{B}$
and $\hat{C}$ mutually commute, $\hat{\sigma}_{2}^{(2)},\hat{\sigma}_{y}^{(2)}$
do not. We used property (b) over both these sets of operators in
the previous step. Returning to the argument, note that $\hat{D}\left|\chi_{G}\right\rangle =-\left|\chi_{G}\right\rangle $,
$\implies m(\hat{D})=-1$ which yields a contradiction. We therefore
conclude that no $m$ with the said properties exists which is consistent
with all predictions of QM.
\end{proof}
